Impact of Water Conditions on Dissolved Oxygen Level

### 2024-04-19 paper/paper.qmd
Update paper.qmd

#IMPORT CLEANED DATA FROM OUTPUTS FOLDER 
water_cleaneddata <- read.csv(here::here("data/cleaned_waterquality_data.csv"),
                  na.strings = c("N/A",""))

@@

#lin_model <- readRDS(file = "/cloud/project/models/linear_model.rds")

>>>>

#IMPORT CLEANED DATA FROM OUTPUTS FOLDER 
water_cleaneddata <- read.csv(here::here("data/cleaned_data/cleaned_waterquality_data.csv"),
                  na.strings = c("N/A",""))

@@

#lin_model <- readRDS(file = "models/linear_model.rds")
